---
title: "Pudding Styled Report"
author: "Your Name"
date: "Last updated: `r format(Sys.time(), '%B %d, %Y')`"
output: 
  puddingR::puddingTheme:
    toc: true
    code_folding: "show"
    number_sections: "false"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Introduction

We've been in the habit lately of leaving our TV on for background noise. Sometimes, if I leave our smart TV on the Netflix app without selecting an account, a screensaver will appear that shows a still image from a show or movie, the title, and 3 descriptive words. Since I've been seeing this frequently, lately, I've started noticing something peculiar...a seemingly large number of shows are described as "irreverent". It's always kind of bothered me, so I wanted to see if there really were a surprisingly large number of shows with that label.

### Load Packages

```{r load_packages}
# For general data cleaning and analysis
library(tidyverse)

# For keeping your files in relative directories
library(here)

# If you want to interact with Google Drive (e.g., upload or download files)
library(googledrive)

# For interactive/searchable tables in your report
library(DT)
```

### Load Data

To collect the data, I just let the screensaver play until it looped, recording the title and descriptive words as it went. Then I created a brand new Netflix profile, didn't give it any input on my preferences and started recording the words for shows on the home screen.

```{r load_gd_2, eval = FALSE}
sheetID <- googledrive::as_id("https://docs.google.com/spreadsheets/d/1cuvIHbH1yhewxldzqwwS0RMQmk1QjfK-J5FSN7z8VFM/edit#gid=0")

googledrive::drive_download(sheetID, 
                            path = here("assets", "data", "raw_data", "netflix.csv"), 
                            overwrite = TRUE)

```

```{r}

netflix <- readr::read_csv(here::here("assets", "data", "raw_data", "netflix.csv")) %>% 
  # remove kids / family movies
  filter(word1 != "children & family" & word2 != "children & family" & word3 != "children & family") %>% 
  filter(word1 != "kids" & word2 != "kids" & word3 != "kids")

write.csv(netflix, "../../web/src/assets/data/shows.csv", row.names = FALSE)
```

## Exploration

### Common Words

Ok, so how many shows are described by the word `irreverent`?

```{r}
netflixLong <- netflix %>% 
  pivot_longer(cols = c("word1", "word2", "word3"), names_to = "position", names_prefix = "word", values_to = "word")

irr <- netflixLong %>% 
  filter(word == "irreverent")
```

Ok, so `r nrow(irr)` of `r nrow(netflix)` shows (`r nrow(irr)/nrow(netflix) * 100`) are described as `irreverent`. That seems high...

Which words are most commonly used?

```{r}
common <- netflixLong %>% 
  count(word) %>% 
  arrange(desc(n)) 

topCommon <- head(common, 15)

write.csv(topCommon, "../../web/src/assets/data/common.csv", row.names = FALSE)
```
 Irreverent is the most common word!! Whyyyyy.
 
### Network

Are the same combinations of words used more than once?

```{r}
sorted <- netflix %>% 
  rowwise() %>% 
  #mutate(sorted = paste0(c(word1, word2, word3), collapse = "-"))
  mutate(sorted = paste0(sort(c(word1, word2, word3)), collapse = "-")) %>% 
  count(sorted)
```

Nope! Each show appears to have a unique combination of 3 words. So now to find out which used are together. 

This is probably the least efficient way to do this, but it'll work


```{r}
m12 <- netflix %>% 
  select(c(word1, word2))

m13 <- netflix %>% 
  select(c(word1, word3)) %>% 
  rename(word2 = word3)

m23 <- netflix %>% 
  select(c(word2, word3)) %>% 
  rename(word1 = word2, word2 = word3)

m21 <- netflix %>% 
  select(c(word2, word1)) %>% 
  rename(word3 = word1, word1 = word2) %>% 
  rename(word2 = word3)

m31 <- netflix %>% 
  select(c(word3, word1)) %>% 
  rename(word2 = word1, word1 = word3)

m32 <- netflix %>% 
  select(c(word3, word2)) %>% 
  rename(word1 = word3)

all <- rbind(m12, m13, m23, m21, m31, m32) %>% 
  group_by(word1, word2) %>% 
  count() 

allTotal <- rbind(m12, m13, m23, m21, m31, m32) %>% 
  distinct() %>% 
  group_by(word1) %>% 
  count()  %>% 
  arrange(desc(n))

allWide <- all %>% 
  pivot_wider(id_cols = "word1", names_from = "word2", values_from = "n")

write.csv(allWide, "../../web/src/assets/data/relation.csv", row.names = FALSE, na = "NULL")

head(allTotal, 10)
```

Ok, so, so far, `irreverent` is the most used word, but also used in combination with the most other words. So, it has the least consistent usage...

```{r}
irrOther <- rbind(m12, m13, m23, m21, m31, m32) %>% 
  filter(word1 == "irreverent") %>% 
  distinct()

irrOther$word2
```

It also (subjectively speaking) is the most difficult word. Words like `witty`, `comedy`, `cynical` and `drama` are all pretty straightforward, but I have to google `irreverent` everytime I see it used as a descriptor. Overall, I just want to know why Netflix uses this term so much. 

Afterall, the definition is: 

> showing a lack of respect for people or things that are generally taken seriously.

But if everything is irreverent, is anything reverent? 

